### 2020-10-13 introduction.tex
logic -> CLL

With regards to $\pi$-calculus, a growing line of work on deadlock freedom leverages the Curry-Howard correspondences between (intuitionistic or classical) linear logic and session-typed $\pi$-calculus \cite{cairespfenning10,wadler12}, which guarantee deadlock freedom by design. This is achieved by the cut rule, which merges together constructs for parallel composition and restriction thus forcing processes to share only one channel for communication and eliminating cyclic dependencies. Recent developments in the Classical Process \cite[CP]{wadler12} line of work have led to various approaches to decoupling these constructs, either by maintaining a strong correspondence to logic, as in Hypersequent CP~\cite[HCP]{kokkemontesi19popl,kokkemontesi19tlla}, or by weakening the correspondence to logic in exchange for a more expressive language, as in Priority CP~\cite[PCP]{dardhagay18}. PCP decouples CP's cut rule into two separate constructs, for parallel composition --- by  introducing a mix rule, and for restriction --- by introducing a cycle rule. Differently from previous work, PCP allows for cyclic structures and restores deadlock freedom by adding priorities to types following Kobayashi~\cite{kobayashi06} and Padovani \cite{padovani14}. Priorities capture the readiness of an action to fire, thus they establish an order of actions in a $\pi$-calculus process.

>>>>

With regards to $\pi$-calculus, a growing line of work on deadlock freedom leverages the Curry-Howard correspondences between (intuitionistic or classical) linear logic and session-typed $\pi$-calculus \cite{cairespfenning10,wadler12}, which guarantee deadlock freedom by design. This is achieved by the cut rule, which merges together constructs for parallel composition and restriction thus forcing processes to share only one channel for communication and eliminating cyclic dependencies. Recent developments in the Classical Process \cite[CP]{wadler12} line of work have led to various approaches to decoupling these constructs, either by maintaining a strong correspondence to classical linear logic, as in Hypersequent CP~\cite[HCP]{kokkemontesi19popl,kokkemontesi19tlla}, or by weakening the correspondence to classical linear logic in exchange for a more expressive language, as in Priority CP~\cite[PCP]{dardhagay18}. PCP decouples CP's cut rule into two separate constructs, for parallel composition --- by  introducing a mix rule, and for restriction --- by introducing a cycle rule. Differently from previous work, PCP allows for cyclic structures and restores deadlock freedom by adding priorities to types following Kobayashi~\cite{kobayashi06} and Padovani \cite{padovani14}. Priorities capture the readiness of an action to fire, thus they establish an order of actions in a $\pi$-calculus process.
